% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Mike Xiangyu Liu}
\newcommand{\CVTitle}{Mike Xy Liu CV updated in Dec 2020}
\newcommand{\CVNote}{Mike Xy Liu CV updated in Dec 2020}
\newcommand{\CVWebpage}{http://www.example.com/~johndoe}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
%pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}


\begin{filecontents*}{ref.bib}
	@misc{test,
		title= "The title",
		howpublished= "Publisher"
	}
\end{filecontents*}
\usepackage{etoolbox}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
     
\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
\par
\href{xiangyu002@e.ntu.edu.sg}
{EMail: xiangyu002@e.ntu.edu.sg}
\,\SubBulletSymbol\,
Tel: +86\,19857155986
\,\SubBulletSymbol\,
\href{\CVWebpage}
{WeChat: lxy13438107982}
\end{SubTitle}

\begin{Body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry
{\textbf{Nanyang Technological University}(NTU)},
Singapore

\BulletItem
M.Sc.. in
{Computer Control and Automation}
\hfill
\DatestampYM{2018}{08} --
\DatestampYM{2019}{06}
\begin{Detail}
\SubBulletItem
Dissertation:
{Quantitative Trajectory Evaluation Criterion and Long-term Enhancement for Multi-Robot SLAM\cite{xiangyu2019quantitative}}
\SubBulletItem
Adviser:
Prof. Danwei Wang
\SubBulletItem
Focus:
Multi-Robot SLAM, Computer Vision.
\SubBulletItem
Cumulative GPA: 3.88 / 5.0
\end{Detail}

\BigGap
\Entry
{\textbf{University of Electronic Science and Technology of China}(UESTC)},
Chengdu, Sichuan, P.R.China

\BulletItem
B.Mgt. in 
{Electronic Commerce}
\hfill
\DatestampYM{2014}{09} --
\DatestampYM{2018}{06}
\BulletItem
B.Eng. in 
{Electronic Engineering}
\begin{Detail}
\SubBulletItem
Dissertation:
	{Research on Organizational Attraction of JD.COM in the era of Smart Logistics \cite{lxybachelor2018}}
\SubBulletItem
Recommended Postgraduate Qualification,
\SubBulletItem
Cumulative GPA: 3.47 / 4.00
\end{Detail}

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\Section
{Skills}
{Skills}
{PDF:Skills}

\Entry
\BulletItem
Excellent in C/C++, Linux, ROS; Skilled in Python, Matlab.
\BulletItem
Excellent in robotics perception and navigation.
\BulletItem
Good understanding in neural network, course-attending in control theory, control network, etc.
\BulletItem
Abundant hands-on experience in robot development.

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% AWARDS & SCHOLARSHIPS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Awards \&\newline
	Scholarships}
{Awards \& Scholarships}
{PDF:AwardsAndScholarships}

\Entry
\textbf{National First Award},
in National University Electronics Design Contest(NUEDC), 
MoE China

\BulletItem
For contest project: panel-ball controlling device
\hfill
\DatestampYM{2017}{8}

\Gap
\Entry
\textbf{National Champion},
in RoboMasters National University Robot Contest,
MoE China \& DJI
\BulletItem
For contest project: RM series robots.
\hfill
\DatestampYM{2015}{10} --
\DatestampYM{2016}{8}

\Gap
\Entry
\textbf{National Bronze Award},
in JD X Robot Challenge Contest,
JD.COM
\BulletItem
For contest project: Automatic Sorting Robot
\hfill
\DatestampYM{2017}{04}

\Gap
\Entry
\textbf{Awards and Scholarships}, 
in several university-level contests held in UESTC

\hfill
\DatestampYM{2014}{09} --
\DatestampYM{2018}{06}

\Gap
\Entry
\textbf{Recommended Postgraduate Qualification},
in UESTC
\BulletItem
For accumulated outstanding performance in national and provincial contests
\hfill
\DatestampYM{2017}{09}


%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Projects}
{Projects}
{PDF:Projects}

\Entry
{\textbf{Computer Vision Group}},
State Key Lab of CAD\&CG, Zhejiang University

\BulletItem
Research Assistant
\hfill
\DatestampYM{2020}{07} --
\DatestampYM{2021}{04}
\begin{Detail}
\SubBulletItem
Project:
Multi Robot Localization, Reconstruction and Exploration
\SubBulletItem
Supervisors:
Prof. Guofeng Zhang
\SubBulletItem
Focus:
Multi-Robot SLAM, Cross-Robot Localization, Dense Reconstruction, Navigation
\end{Detail}

\Gap
\Entry
{\textbf{Robotics ADVANCe Laboratory}},
NTU

\BulletItem
Master Dissertation
\hfill
\DatestampYM{2018}{10} --
\DatestampYM{2019}{04}
\begin{Detail}
\SubBulletItem
Project:
Place Recognition and Localization for Multi-Robot SLAM \cite{xiangyu2019quantitative}
\SubBulletItem
Supervisors:
Prof. Danwei Wang
\SubBulletItem
Focus:
SLAM, Multi-Robot SLAM, Computer Vision
\end{Detail}

\Gap
\Entry
{\textbf{RoboMasters Contest Lab}},
UESTC

\BulletItem
RoboMasters Contest Robot Design
\hfill
\DatestampYM{2015}{10} --
\DatestampYM{2016}{08}
\begin{Detail}
	\SubBulletItem
	Project:
	UAV for RM Contest
	\SubBulletItem
	Supervisors:
	Prof. Liping He
	\SubBulletItem
	Focus:
	Robot Contest, Computer Vision, Target Recognition, Item Grabbing
	\SubBulletItem
	Patent:
	A UAV-mounted lightweight grabbing device
	
\end{Detail}

\BulletItem
JDX Robot Challenge \cite{lxyjd2017}
\hfill
\DatestampYM{2017}{01} --
\DatestampYM{2017}{04}
\begin{Detail}
	\SubBulletItem
	Project:
	Auto-sorting robot
	\SubBulletItem
	Supervisors:
	Prof. Liping He
	\SubBulletItem
	Focus:
	Robot Contest, 3D Vision, Target Recognization, Item Grabbing
\end{Detail}

\BulletItem
National University Electronic Design Contest
\hfill
\DatestampYM{2017}{08} 
\begin{Detail}
	\SubBulletItem
	Project:
	Panel-ball Control Device
	\SubBulletItem
	Supervisors:
	Prof. Jiexiong Ding
	\SubBulletItem
	Focus:
	Robot Contest, Target Recognization, Control
\end{Detail}

\Gap
\Entry
{\textbf{JD.COM X Department}}, JD.COM

\BulletItem
Internship, Embedded Algorithm Engineer
\hfill
\DatestampYM{2017}{09} --
\DatestampYM{2017}{12}
\begin{Detail}
	\SubBulletItem
	Project:
	Auto-Warehouse AGV
	\SubBulletItem
	Work: Joined the R\&D group of auto-warehouse AGVs, help to design and debug AGVs for smart logistic application.
	\SubBulletItem
	Focus:
	Smart Logistics, AGV.
\end{Detail}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OTHER WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Work\newline
	Experience}
{Work Experience}
{PDF:WorkExperience}

\Entry
{\textbf{Nanyang Technological University}},
Singapore

\BulletItem
Research Associate,
Robotic Lab
\hfill
\DatestampYM{2021}{07} --
Now
\begin{Detail}
	\SubBulletItem
	Supervisor:
	Prof. Danwei Wang
\end{Detail}

\Gap
\Entry
{\textbf{Zhejiang University}},
Hangzhou, China

\BulletItem
Research Assistant,
State Key Lab of CAD\&CG,
College of Computer Science
\hfill
\DatestampYM{2020}{07} --
\DatestampYM{2021}{04}
\begin{Detail}
	\SubBulletItem
	CAD\&CG: Computer Aided Design and Computer Graphics
	\SubBulletItem
	Project: Multi Robot Collaborative SLAM
	\SubBulletItem
	Supervisors:
	Prof. Guofeng Zhang
\end{Detail}

\Gap
\Entry
{\textbf{Nanyang Technological University}},
Singapore

\BulletItem
Research Associate,
NTU-Siemens Cooperative Lab, ERIAN
\hfill
Aborted
\begin{Detail}
	\SubBulletItem
	Before the commence date of the job, my work pass application was rejected by MOM, due to the COVID-19 situation. And as a consequence, the job offer was withdrawn.
\end{Detail}

%%%%%%%%%%%%%%%%%%%%%%%
%% CAMPUS ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Campus Activities}
{Campus Activities}
{PDF:CampusActivities}

\Entry
{\textbf{Work-Zone of Innovation And Entrepreneurship}},
School of Management and Economics, 
UESTC

\BulletItem
Chief Manager
\hfill
\DatestampYM{2015}{07} --
\DatestampYM{2017}{09}
\begin{Detail}
\SubBulletItem
Improved the talent-training concept and mechanism.
\SubBulletItem
Led the team to finish 11 university-level projects, and won over 10 prizes including 3 national
 and 1 provincial prizes.
\end{Detail}

\Gap
{\textbf{Gymguys Training and Fitness Company}},
Chicago, 
USA

\BulletItem
Internship
\hfill
\DatestampYM{2015}{07} --
\DatestampYM{2015}{08}
\begin{Detail}
	\SubBulletItem
	Marketing work as an assistant of the marketing director.
\end{Detail}

\Gap
{\textbf{SMU Entrepreneurship Program}},
Singapore Management University,
Singapore

\BulletItem
Course Program
\hfill
\DatestampYM{2016}{01} --
\DatestampYM{2016}{02}
\begin{Detail}
\SubBulletItem
Attended SMU entrepreneurship courses, including innovation mind, entrepreneurship management, and team management, etc.
\SubBulletItem
Finished the business plan training program with the entrepreneurship idea of “THE LAST MILE”,which was focusing on problems of O2O delivery.
\end{Detail}


%%%%%%%%%%%%%%%
%% LANGUAGES %%
%%%%%%%%%%%%%%%

\Section
{Languages}
{Languages}
{PDF:Languages}

\BulletItem
Chinese: Native speaker.

\Gap
\BulletItem
English: Fluent (IELTS: 6.5(6)).


%%%%%%%%%%%%%%%%
%% REFERENCES %%
%%%%%%%%%%%%%%%%

\Section
{References}
{References}
{PDF:References}

\Gap
\BulletItem
\textbf{Dr Danwei WANG, Professor}
\newline
Division of Control and Instrumentation,
School of Electrical and Electrical Engineering, Block S2
\newline
Nanyang Technological University,
Nanyang Avenue, Singapore 639798
\newline
Office phone: (+65) 6790 5376
\newline
School fax: (+65) 6793 3318
\newline
E-mail: \url{edwwang@ntu.edu.sg}
\newline
WWW: \url{http://www.ntu.edu.sg/home/edwwang}


\BulletItem
\textbf{Dr Guofeng ZHANG, Professor}
\newline
Computer Vision Group, State Key Lab of CAD\&CG
\newline
East Building 1A-509, ZijinGang Campus, Zhejiang University
\newline
Office phone: (+86) 571-88208701
\newline
School fax: (+86) 571-88206680
\newline
E-mail: \url{zhangguofeng@cad.zju.edu.cn}
\newline
WWW: \url{http://www.cad.zju.edu.cn/home/gfzhang}


\Gap
\BulletItem
\textbf{Dr Liping HE, Professor}
\newline
PhD, Professor, School of Mechatronics Engineering,
\newline
University of Electronic Science and Technology of China,
\newline
Tel.: +86-18118010621
\newline
Email: \url{lipinghe@uestc.edu.cn}
\newline
Address: No.2006, Xiyuan Ave, West Hi-tech Zone, 611731 Chengdu, Sichuan, P. R. China

%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%%

\Section
{Publications}
{Publications}
{PDF:Publications}

% Declare a new group to limit the scope of \MaxNumberedItem to this subsection.
\begingroup
\renewcommand{\MaxNumberedItem}{[88]}

\nocite{*}
\bibliographystyle{plain}
\bibliography{ref}

\endgroup


\end{Body}

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

\UseNoteFont%
\null\hfill%

\end{document}
